Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-04-14 paper/abstraction/paper.tex
fix weird overflow issue

Our results are encouraging for these settings. Our abstractions are perfectly expressive for all tree-based topologies---we did not have to fix any aspect of their structure---and the analysis is precise in all cases.

>>>>

Our results are encouraging for these settings. Our abstractions are perfectly expressive for tree-based topologies---we did not have to fix any aspect of their structure---and the analysis is precise in all cases.
